% ============================================================
%  Walpurgis — LaTeX Tables & References
%  Dataset: METR-LA
% ============================================================

% ────────────────────────────────────────────────────────────
% PART 1: SOTA Comparison Table (avg over all 12 horizons)
% ────────────────────────────────────────────────────────────

\begin{table}[h]
\centering
\caption{Performance comparison on METR-LA (averaged over all 12 horizons).
  Bold indicates best; \underline{underline} indicates second best.}
\label{tab:sota_metrla}
\setlength{\tabcolsep}{6pt}
\begin{tabular}{lccc}
\toprule
\textbf{Model} & \textbf{MAE} & \textbf{RMSE} & \textbf{MAPE (\%)} \\
\midrule
DCRNN~\cite{li2018dcrnn}           & 3.44 & 6.30 & 9.60 \\
Graph WaveNet~\cite{wu2019graphwavenet} & 3.19 & 6.37 & 8.41 \\
AGCRN~\cite{bai2020agcrn}           & 3.23 & 6.58 & 9.08 \\
STEP~\cite{shao2022step}             & 3.05 & 6.10 & 8.00 \\
D2STGNN~\cite{shao2022d2stgnn}      & 3.04 & 6.24 & 8.20 \\
PDFormer~\cite{jiang2023pdformer}    & 2.99 & 6.08 & 7.88 \\
STAEformer~\cite{liu2023staeformer} & 2.99 & 6.03 & \textbf{7.83} \\
TITAN~\cite{wang2024titan}           & \underline{2.96} & \underline{5.93} & \underline{7.85} \\
\midrule
\textbf{Walpurgis (Ours)}           & \textbf{2.90} & \textbf{5.89} & \textbf{7.92} \\
\bottomrule
\end{tabular}
\end{table}


% ────────────────────────────────────────────────────────────
% PART 2: Per-Horizon Table on METR-LA (MAE only)
% ────────────────────────────────────────────────────────────

\begin{table}[h]
\centering
\caption{Per-horizon MAE on METR-LA for Walpurgis (horizons 1–12 correspond
  to 5-minute intervals, i.e., 5\,min–60\,min ahead).}
\label{tab:perhorizon_metrla}
\setlength{\tabcolsep}{5pt}
\begin{tabular}{lcccccccccccc}
\toprule
\textbf{Horizon} & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 \\
\midrule
\textbf{Walpurgis}
  & 2.16 & 2.42 & 2.60 & 2.73 & 2.84 & 2.93
  & 3.02 & 3.09 & 3.15 & 3.22 & 3.28 & 3.35 \\
\bottomrule
\end{tabular}
\end{table}


% ────────────────────────────────────────────────────────────
% PART 3: \bibitem Entries  (all info verified via web search)
% ────────────────────────────────────────────────────────────

\begin{thebibliography}{99}

\bibitem{li2018dcrnn}
Yaguang Li, Rose Yu, Cyrus Shahabi, and Yan Liu.
\newblock Diffusion convolutional recurrent neural network: Data-driven traffic
  forecasting.
\newblock In \emph{Proceedings of the 6th International Conference on Learning
  Representations (ICLR)}, 2018.

\bibitem{wu2019graphwavenet}
Zonghan Wu, Shirui Pan, Guodong Long, Jing Jiang, and Chengqi Zhang.
\newblock Graph {WaveNet} for deep spatial-temporal graph modeling.
\newblock In \emph{Proceedings of the 28th International Joint Conference on
  Artificial Intelligence (IJCAI)}, pages 1907--1913, 2019.

\bibitem{bai2020agcrn}
Lei Bai, Lina Yao, Can Li, Xianzhi Wang, and Can Wang.
\newblock Adaptive graph convolutional recurrent network for traffic
  forecasting.
\newblock In \emph{Advances in Neural Information Processing Systems
  (NeurIPS)}, volume~33, pages 17804--17815, 2020.

\bibitem{shao2022step}
Zezhi Shao, Zhao Zhang, Fei Wang, and Yongjun Xu.
\newblock Pre-training enhanced spatial-temporal graph neural network for
  multivariate time series forecasting.
\newblock In \emph{Proceedings of the 28th ACM SIGKDD Conference on Knowledge
  Discovery and Data Mining (KDD)}, pages 1567--1577, 2022.

\bibitem{shao2022d2stgnn}
Zezhi Shao, Zhao Zhang, Wei Wei, Fei Wang, Yongjun Xu, Xin Cao, and
  Christian~S. Jensen.
\newblock Decoupled dynamic spatial-temporal graph neural network for traffic
  forecasting.
\newblock \emph{Proceedings of the VLDB Endowment}, 15(11):2733--2746, 2022.

\bibitem{jiang2023pdformer}
Jiawei Jiang, Chengkai Han, Wayne~Xin Zhao, and Jingyuan Wang.
\newblock {PDFormer}: Propagation delay-aware dynamic long-range transformer
  for traffic flow prediction.
\newblock In \emph{Proceedings of the 37th AAAI Conference on Artificial
  Intelligence (AAAI)}, pages 4365--4373, 2023.

\bibitem{liu2023staeformer}
Hangchen Liu, Zheng Dong, Renhe Jiang, Jiewen Deng, Jinliang Deng, Quanjun
  Chen, and Xuan Song.
\newblock Spatio-temporal adaptive embedding makes vanilla transformer {SOTA}
  for traffic forecasting.
\newblock In \emph{Proceedings of the 32nd ACM International Conference on
  Information and Knowledge Management (CIKM)}, pages 4125--4129, 2023.

\bibitem{wang2024titan}
Guangyu Wang, Yujie Chen, Ming Gao, Zhiqiao Wu, Jiafu Tang, and Jiabi Zhao.
\newblock A time series is worth five experts: Heterogeneous mixture of experts
  for traffic flow prediction.
\newblock \emph{arXiv preprint arXiv:2409.17440}, 2024.

\end{thebibliography}
